Cosmological Evidences of Dark Matter through the CMB

### 2018-12-23 paper/main.tex
bib changed

\section{Introduction}
Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally. 
Therefore, scientists have proposed the existence of a new form of matter that does not interact electromagnetically but gravitationally: Dark Matter.
Neverthless the fundamental nature of Dark Matter is not well understood, there are strong evidences for the existence of Dark Matter. 
One of the most important evidence of the existance of Dark Matter comes from the analysis of the Cosmic Microwave Background.

Since Dark Matter does not interact electromagnetically, its existence has been animatedly discussed.

-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\section{From the Discovery of the CMB to the Planck mission}
\citep{bucherPhysicsCosmicMicrowave2015}
-discovery of the cmb\\
-filterng of the images\\
-different missions\\

@@

\bibliographystyle{plain}
\bibliography{dark}
\end{document}

>>>>

\section{Introduction}
Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally. 
Therefore, scientists have proposed the existence of a new form of matter that does not interact electromagnetically but gravitationally: Dark Matter.
Nevertheless the fundamental nature of Dark Matter is not well understood, there are strong evidences for the existence of Dark Matter. 
One of the most important evidence for the existence of Dark Matter comes from the analysis of the Cosmic Microwave Background (CMB). \\
The Cosmic Microwave Background is the electromagnetic radiation coming from the hot plasma of the early stages of the Universe.
When the Universe, made of hot plasma, reached a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$, the number density of the free electrons dropped, causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple. They have since streamed freely through the universe and are today observed as the cosmic microwave background \citep{LecturesPdf}

-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\section{From the Discovery of the CMB to the Planck mission}
The early Universe was made of a hot and dense plasma made that cooled down as the Universe was expanding. At $T= 100$ GeV  particles receive their masses through the Higgs mechanism

-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\

\citep{bucherPhysicsCosmicMicrowave2015}
-discovery of the cmb\\
-filterng of the images\\
-different missions\\

@@

\bibliographystyle{plain}
\bibliography{dark_1}
\end{document}
